The expected shape of the Milky Way's Dark Matter halo

### 2019-01-27 Paper/paper.tex
Quick Plot descriptions: To improve later

\begin{figure*}
  \centering
  \subfloat[halo 27 DM shape at small radius]{\includegraphics[width=0.5\textwidth]{./pics/MHD_Vs_DM/level4_DM_halo_27_inner.png}}
  \hfill
  \subfloat[halo 27 DM shape at big radius]{\includegraphics[width=0.5\textwidth]{./pics/MHD_Vs_DM/level4_DM_halo_27_outter.png}}
  \hfill
  \caption{DM density for inner/outer (left/right panel) DM halo regions.}
  \label{fig:slices}
\end{figure*}

@@

\begin{figure}
\centering
{\includegraphics[width=0.8\columnwidth]{./pics/halo16.png}}
\caption{Radial profile for axial ratios and the triaxiality parameter $T=\frac{1-b/a}{1-c/a}$ for halo 16.}
\label{fig:DM_MHD}
\end{figure}

@@

  \hfill
  \caption{Shape of each halo on the plane $c/a$ Vs $b/a$. Errorbar shows median and errors for each sampled radii. }
  \label{fig:Triax_DM}
\end{figure}

@@

\begin{figure}
  \centering
 \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_MHD.png}
  \hfill
  \caption{Shape of each halo on the plane $c/a$ Vs $b/a$. Errorbar
    shows median and errors for each sampled radii. } 
  \label{fig:Triax_MHD}
\end{figure}

@@

\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{./pics/Delta asphericity Vs Star Density.png}
    \caption{Difference in asphericities between MHD and DM shapes Vs Star Density of the simulation.}
    \label{fig:Star_Density_effect}
\end{figure}

@@

\begin{figure}
  \centering
  \subfloat[halo 16 DM]{\includegraphics[width=0.5\columnwidth]{./pics/Redshift/halo_16_level3_DM_Z.png}}
  \hfill
  \subfloat[halo 16 MHD]{\includegraphics[width=0.5\columnwidth]{./pics/Redshift/halo_16_level3_MHD_Z.png}}
  \caption{Radial profile (comoving) of axial ratios for halo 16 in terms of redshift (color). This halo maintains its shape until $z\approx 1$ obviating the systematic rounding effect in time from asymmetric potentials. }
  \label{fig:RedshiftGood}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{./pics/Redshift/halo_27_DM_Z_correlation.png}
    \caption{Difference in asphericities between MHD and DM shapes Vs Star Density of the simulation.}
    \label{fig:DM Z Triax}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{./pics/Redshift/halo_24_level3_MHD_Z_Triax.png}
    \caption{Difference in asphericities between MHD and DM shapes Vs
      Star Density of the simulation.} 
    \label{fig:MHD Z Triax} 
\end{figure}

@@

\begin{figure}
  \centering
  \subfloat[Perfectly aligned Axes]{\includegraphics[width=1\columnwidth]{./pics/well_axes.png}}
  \hfill
  \subfloat[Somewhat aligned Axes]{\includegraphics[width=1\columnwidth]{./pics/rotating_axes.png}}
  \hfill
  \subfloat[Chaotic Axes]{\includegraphics[width=1\columnwidth]{./pics/chaotic_axes.png}}
  \hfill
  \caption{Description of axes alignments }
  \label{fig:alignment}
\end{figure}

>>>>

\begin{figure*}
  \centering
  \subfloat[halo 27 DM shape at small radius]{\includegraphics[width=0.5\textwidth]{./pics/MHD_Vs_DM/level4_DM_halo_27_inner.png}}
  \hfill
  \subfloat[halo 27 DM shape at big radius]{\includegraphics[width=0.5\textwidth]{./pics/MHD_Vs_DM/level4_DM_halo_27_outter.png}}
  \hfill
  \caption{DM density for inner/outer (left/right panel) DM halo regions.

  Slice 20 percent of the max-min range in the "z" position of particles belonging to the main structure, centered at halo defined position (calculated with most bounded particle) }
  % definition of the input positions
  % Gets the length of the main structure particles /// 0 - Principal halo, 1 - DM
  %  cut = subSn.group.GroupLenType[0,1]
  % graphs are calculated using the following YT command
  % p = yt.ProjectionPlot(ds, 'z', nn_density, center=c, weight_field=nn_density, width=(0.2*(npos.max()-npos.min()), 'kpc'))

  \label{fig:slices}
\end{figure*}

@@

\begin{figure}
\centering
{\includegraphics[width=0.8\columnwidth]{./pics/halo16.png}}
\caption{Radial profile for axial ratios and the triaxiality parameter $T=\frac{1-b/a}{1-c/a}$ for halo 16.

Radial profile was sampled at redshift 0 and there are two sets of lines showing MHD and DM-only versions of the axial ratios profile}
\label{fig:DM_MHD}
\end{figure}

@@

  \hfill
  \caption{Shape of each halo on the plane $c/a$ Vs $b/a$. (DM only)\\
   Each dot represents the shape characterization of each halo at the 2 times the virial radius and a  1/16 fraction of the virial radius differentiated by color.\\   
  Errorbar shows median and errors for each sampled radii.\\
  Conclusion: DM halos are rounder on the outerskirts }
  \label{fig:Triax_DM}
\end{figure}

@@

\begin{figure}
  \centering
 \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_MHD.png}
  \hfill
  \caption{Shape of each halo on the plane $c/a$ Vs $b/a$. (MHD only)\\
   Each dot represents the shape characterization of each halo at the 2 times the virial radius and a  1/16 fraction of the virial radius differentiated by color.\\   
  Errorbar shows median and errors for each sampled radii.\\
  Conclusion: MHD halos are more oblate on the outer skirts: b/a changes while c/a remains practically constant (on average) } 
  \label{fig:Triax_MHD}
\end{figure}

@@

\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{./pics/Delta asphericity Vs Star Density.png}
    \caption{Difference in asphericities between MHD and DM shapes Vs Star Density of the simulation.\\
    Unsure about this graphic.\\
    Take delta asphericity as the strength of the rounding effect of baryons.}
    \label{fig:Star_Density_effect}
\end{figure}

@@

\begin{figure}
  \centering
  \subfloat[halo 16 DM]{\includegraphics[width=0.5\columnwidth]{./pics/Redshift/halo_16_level3_DM_Z.png}}
  \hfill
  \subfloat[halo 16 MHD]{\includegraphics[width=0.5\columnwidth]{./pics/Redshift/halo_16_level3_MHD_Z.png}}
  \caption{Radial profile (comoving) of axial ratios for halo 16 in terms of redshift (color). This halo maintains its shape until $z\approx 1$ obviating the systematic rounding effect in time from asymmetric potentials.\\

Each plot-line represents the radial profile at a determined redshift.\\
Conclussion: Mainly for b/a, it increases for:\\ (1) for bigger radii (fixed redshift) \\
												 (2) for lower redshift (fixed radius)\\

It explains the correlation between radial profile and history, but does not require that curves match in the triaxial plane.  }
  \label{fig:RedshiftGood}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{./pics/Redshift/halo_27_DM_Z_correlation.png}
    \caption{DM only\\
    		 Radial profile at redshift 0 (dashed line)\\
    		 Historical profile at virial radius R500 (colour line)\\
    		 Example of a halo where there is some correlation between these two profiles, as usually happens for DM only simulations.\\
    		 Conclusion: DM only halos usually (fraction?) have correlated shape profiles 
    		 }
    \label{fig:DM Z Triax}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{./pics/Redshift/halo_24_level3_MHD_Z_Triax.png}
    \caption{MHD\\
    		 Radial profile at redshift 0 (dashed line)\\
    		 Historical profile at virial radius R500 (colour line)\\
    		 Example of a halo where there is no correlation between these two profiles, as usually happens in MHD\\
    		 Conclusion: MHD halos usually (fraction?) have uncorrelated shape profiles 
    		 } 
    \label{fig:MHD Z Triax} 
\end{figure}

@@

\begin{figure}
  \centering
  \subfloat[Perfectly aligned Axes]{\includegraphics[width=1\columnwidth]{./pics/well_axes.png}}
  \hfill
  \subfloat[Somewhat aligned Axes]{\includegraphics[width=1\columnwidth]{./pics/rotating_axes.png}}
  \hfill
  \subfloat[Chaotic Axes]{\includegraphics[width=1\columnwidth]{./pics/chaotic_axes.png}}
  \hfill
  \caption{Star: Minor Axis\\
  		   Triangle: Medium Axis\\
  		   Square: Major Axis\\
  		   Color: Radii at which shape was sampled (show radii sampled)\\
  		   Contour color: If orientation is above or below in this projection\\
  		   Cross (black): Orientation of the stellar disk\\
  		   Conclusion: Axes (minor) are not (generally) aligned with the stellar disk nor are they usually aligned with each other from different radii. We show some cases that may happen\\  }
  \label{fig:alignment}
\end{figure}
